Extracting Application and Menu Events from UI Tutorial Videos

### 2015-05-12 paper/main.tex
Minor fixes

Perhaps most related, Waken~\cite{banovic_waken_2012}
contributes to this research direction by discovering cursor shapes, clicking actions, icons, tooltips and
menus, all by examining the difference between frames of UI video.  They do this by making
assumptions about how the image of icons change during hover and press actions.  Detection of the
cursor and icons in later frames is performed by template matching.  We rely on techniques similar
to those in Waken to detect when and where menus appear in UI videos.

@@

\begin{figure}[t]
\centering
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{AlexNet_Accuracy1000}
  \caption{AlexNet accuracy results of two networks trained on two image datasets.}
  \label{fig:alex_net}
  \end{minipage}\hfill
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{PerClassPerformance1000}
  \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
  \label{fig:per_class}
  \end{minipage}
\end{figure}

@@

\begin{figure}[t]
\centering
  \begin{minipage}{.35\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All1000}
  \caption{Visualization of filters from the network trained on all our image data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.35\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}

>>>>

Perhaps most related, Waken~\cite{banovic_waken_2012}
contributes to this research direction by discovering cursor shapes, clicking actions, icons, tooltips and
menus, all by examining the difference between frames of UI videos.  They do this by making
assumptions about how the image of icons change during hover and press actions.  Detection of the
cursor and icons in later frames is performed by template matching.  We rely on techniques similar
to those in Waken to detect when and where menus appear in UI videos.

@@

\begin{figure}[t]
\centering
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{AlexNet_Accuracy1000}
  \caption{AlexNet accuracy results of two networks trained on two image datasets.}
  \label{fig:alex_net}
  \end{minipage}\hfill
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{PerClassPerformance1000}
  \caption{AlexNet per-class accuracy results for our ``noiseless'' network.}
  \label{fig:per_class}
  \end{minipage}
\end{figure}

@@

\begin{figure}[t]
\centering
  \begin{minipage}{.35\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All1000}
  \caption{Visualization of filters from the network trained on all data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.35\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
  \caption{Visualization of filters from the network based on ``no noise'' data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}
